WORCS: A Workflow for Open Reproducible Code in Science

### 2020-10-28 paper/Manuscript_DS.Rmd
explain why renv is more userfriendly than docker

For analyses conducted entirely in `R`, the recently released package `renv`
strikes a great balance between user-friendliness  and effectiveness. Developed by
the team behind RStudio, this package simply maintains a text-based,
human-readable log of all packages used, their version numbers, and where they
were installed from (e.g., CRAN, Bioconductor, GitHub). As long as these
repositories maintain their archives, this solution is reliable and very
lightweight.
The text-based log file can be version controlled with Git. `renv`
installs the logged packages in a cache that is shared between all
projects on the computer. Thus, if one of your projects uses a package that is
already in the cache, it does not
need to be installed again. This prevents long installation
times, large space requirements, and frustration having to re-install software
that is already installed on the system. When someone else loads your 
project, `renv` will install all of the required packages onto a cache on their
computer. 
This is not a foolproof method to ensure strict computational reproducibility, but it is more user-friendly
and lightweight than any alternative out there, requiring no technical skill to
setup. When choosing an appropriate solution for dependency management, it is
important to consider that all solutions have a limited shelf life
[@brownHowLearnedStop2017].
Ultimately, the best approach might be to use a "good-enough" solution, and
acknowledge that all code requires some maintenance if you want to
reproduce it in the future. For projects in `R`, `renv` meets these requirements.

>>>>

For analyses conducted entirely in `R`, the recently released package `renv`
strikes a great balance between user-friendliness  and effectiveness. Developed by
the team behind RStudio, this package simply maintains a text-based,
human-readable log of all packages used, their version numbers, and where they
were installed from (e.g., CRAN, Bioconductor, GitHub). As long as these
repositories maintain their archives, this solution is reliable and very
lightweight.
The text-based log file can be version controlled with Git. `renv`
installs the logged packages in a cache that is shared between all
projects on the computer. Thus, if one of your projects uses a package that is
already in the cache, it does not
need to be installed again. This prevents long installation
times, large space requirements, and frustration having to re-install software
that is already installed on the system. When someone else loads your 
project, `renv` will install all of the required packages onto a cache on their
computer. As opposed to the alternatives `renv` is tightly integrated with the
native R package management system and thus does not require the users to change their workflow of installing/removing and using packages.
This is not a fail-safe method to ensure strict computational reproducibility, but it is more user-friendly
and lightweight than any alternative out there, requiring no technical skill to
setup. When choosing an appropriate solution for dependency management, it is
important to consider that all solutions have a limited shelf life
[@brownHowLearnedStop2017].
Ultimately, the best approach might be to use a "good-enough" solution, and
acknowledge that all code requires some maintenance if you want to
reproduce it in the future. For projects in `R`, `renv` meets these requirements.
